\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}

\begin{document}
\name{\Large Tyler Jones}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: (970) 261-9425 \hfill Email: me@tjones.dev  \hfill Github: tjones879\vspace{0mm}\\\vspace{-4.5mm}

    \section{\mysidestyle Work\\Experience}

    \textbf{AMERGINT Technologies} \vspace{1mm}\\\vspace{1mm}%
    \textsl{Systems Engineer, Launch/Range Systems} \hfill \textbf{July 2018 -- Present}\\
      Designed, implemented, and delivered mission-critical and safety-critical systems on strict timelines
      written in C++ and Python.
      \begin{itemize}
      \item Lead the design and development of more than \$8 MM of novel hardware-in-the-loop testing platforms
            for modern hypersonic and missile defense programs.
      \item Designed and implemented a next-generation software-based LDPC decoder architecture capable of
            multi-gigabit downlink rates.
      \item Optimized the performance of telemetry processing decommutation and commutation subsystems
            by up to 20x for use in range safety environments.
      \item Built a new line of IRIG 106 Chapter 10 data recorders for rapid development of
            multi-gigabit data recording and processing product lines.
      \item Lead development of an embedded, network-enabled IO and RF test equipment product line.
      \end{itemize}


    \textbf{FFmpeg} \vspace{1mm}\\\vspace{1mm}%
    \textsl{Google Summer of Code Participant -- Vorbis Encoder} \hfill \textbf{Feb 2017 -- Aug 2017}\\
    Improved the encoding quality and speed of FFmpeg's native Vorbis
    encoder by redesigning major components and implementing new
    psychoacoustic models.

	\begin{itemize}
	\item Built a custom psychoacoustical model capable of detecting
              transient signals and dynamically switching encoding modes.
	\item Implemented noise normalization to generate a perceived gaussian noise
            profile and designed residue encoding to minimize
            quantization error.
	\item Rewrote the stereo coupling to dynamically switch between
	      various lossy and lossless encoding modes.
	\end{itemize}

    \section{\mysidestyle Other\\Projects}

    \textbf{Flying Drone}\\
    Built an autonomous drone from bare components and a custom real-time operating environment.

    \begin{itemize}
      \item Utilized OFDM with a custom packetized protocol for efficient command, control,
            and telemetry in ISM bands.
      \item Built Linux kernel drivers to minimize the latency of subsystem components in centralized
            ground stations.
      \item Developed full environment and sensor simulations for faster iteration of state estimation
            and vehicle localization algorithms.
    \end{itemize}

    \textbf{Stream Processing Language}\\
    Designing a novel compiler and domain specific language for efficient synchronous data flow processing.

    \begin{itemize}
        \item Employed scalar evolution analysis for alias detection and identification of
              instruction-level parallelism.
        \item Designing algorithms for aggressive auto-vectorization and pipelining of numeric code.
        \item Implementing optimized static scheduling of stream processing applications to maintain
              memory locality and efficient cache utilization.
    \end{itemize}

\iffalse
    \textbf{Auto Chess}\\
    Designed a self-contained autonomous chess board with integration with popular chess websites.

    \begin{itemize}
        \item Designed and integrated PCB's for detection and management of board state.
        \item Integrated web API's for play against computer engines and online players.
        \item Developed communication protocols for control of real-time subsystems from an embedded
              Linux platform.
    \end{itemize}
\fi

    \section{\mysidestyle College\\Education}

    \textbf{Colorado Mesa University}, Grand Junction, CO \vspace{1mm}\\\vspace{1mm}%
    \textsl{B.S. Computer Science} GPA - 4.0 \hfill \textbf{Aug 2014 -- May 2018}

    \section{\mysidestyle Technical\\Skills}

    \emph{Languages:} C, C++, Python, Rust\\
    \emph{Tools:} Git/SVN, Valgrind, GCC/LLVM, perf, eBPF, Docker\\
    \emph{Other Knowledge:} Linux and RTOS Kernel Development, Embedded Linux, Software-defined radio\\
\end{resume}
\end{document}
